%%
% Saad Khan Resume
%

%%
% Document configuration
%
\documentclass{article}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{soul}
\usepackage[document]{ragged2e}

\begin{document}
%%
% Some details
%
\begin{center}
    % Name
    {\MakeUppercase{\huge\bf Saad Khan}} \\
    \bigskip
    \hrule
    \bigskip
    % Address
    29 A Hollandale Lane $\diamond$ Clifton Park, NY 12065 \\
    +1 (518)~$\cdot$~389~$\cdot$~5093 $\diamond$ saad.khan02@gmail.com \\
    \bigskip
\end{center}

%%
% Skills
%
\subsection*{\MakeUppercase{\bf Skills}}
    \hrule
    \bigskip
    \begin{tabular}{l l}
    {\bfseries Languages} &
    Perl, AutoIt, bash, IECC-61131, C/C++\\
    \\
    {\bfseries Software} &
    Wonderware, ISaGRAF, Simatic S7, Wireshark, git, Microsoft Office,\\
    &
    Libre Office, nmap, tcpdump \\
    \\
    {\bfseries Hardware} &
    Allen Bradley SLC controllers and PLCs, Siemens Simatic S7,\\
    &
    Sixnet IPms, Red Lion HMIs, EIG Power Quality meters \\
    \\
    {\bfseries Other} &
    Modbus, Sixnet UDR, TCP/IP, DNS, ProfiNET, ProfiBUS, DNP3, \LaTeX, \\
    &
    Doxygen, Markdown, Linux \\
    \end{tabular}
    \bigskip

%%
% Employment history
%
\subsection*{\MakeUppercase{\bf Employment History}}
    \hrule
    \bigskip
    % Sixnet - Red Lion - Associate Software Engineer
    {\bf Sixnet, LLC (Red Lion Controls)} \hfill {\em Mar 2013 - Present} \\
    Test Automation Engineer \hfill {\em Ballston Lake, NY} \\
    \begin{itemize}
    \item \underline{\it Automated testing:}
          \begin{itemize}
          \item Developed and maintained nightly test framework using Perl
                and bash in Linux.
          \item Wrote scripts to test software applications in Windows using
                AutoIt.
          \item Designed and assembled test panels.
          \item Maintained Selenium tests for browser based webserver tests.
          \item Evaluated tools for testing software and hardware products.
          \end{itemize}
    \item \underline{\it Manual testing:}
          \begin{itemize}
          \item Performed manual tests as part of release testing.
          \item Ran device verification tests and automated them as possible.
          \item Built customer specific test rigs to emulate on field testing.
          \item Tested compatibility of Sixnet/Red Lion devices with third
                party automation and network devices.
          \item Worked closely with Technical Support staff to reproduce bugs
                and retest bug fixes before release.
          \end{itemize}
    \end{itemize}
    \bigskip

    % Sixnet - Red Lion - Technical Support Engineer
    {\bf Sixnet, LLC (Red Lion Controls)} \hfill {\em Mar 2011 - Mar 2013} \\
    Technical Support Engineer \hfill {\em Ballston Lake, NY} \\
    \begin{itemize}
    \item \underline{\it RTU programming:}
          \begin{itemize}
          \item Configured RTUs and IO modules as part of developing customer
                applications.
          \item Programmed IO modules, RTUs and HMI panels using Sixnet Tool
                Kit, ISaGRAF and Crimson respectively.
          \item Performed release testing of hardware and software products.
          \end{itemize}
    \item \underline{\it Technical support:}
          \begin{itemize}
          \item Helped customers over phone and email to deploy time and process
                critical industrial automation solutions.
          \item Helped customers with program optimization to decrease cycle
                time and overrun count.
          \item Devised workarounds as temporary solutions in critical
                environments.
          \item Worked closely with Engineering to resolve urgent customer
                issues.
          \end{itemize}
    \item \underline{\it Recognition:}
          \begin{itemize}
          \item Member, MVP Team, Q2 2011
          \end{itemize}
    \end{itemize}
    \bigskip

    % GPDS - Automation Engineer
    {\bf Gulf Power Distribution Systems} \hfill {\em Oct 2007 - Jan 2009} \\
    Automation Engineer \hfill {\em Dammam, Saudi Arabia} \\
    \begin{itemize}
    \item \underline{\it Field implementation:}
          \begin{itemize}
          \item Installed and commissioned power monitoring systems at Tanajib
                onshore facility.
          \item Configured Nexus 1250/1252 power quality meters.
          \item Used DNP3 for communication
          \item Worked with third party teams to establish communication over
                copper and fiber optic between different stations at the onshore
                facility.
          \end{itemize}
    \item \underline{\it Pre-sales:}
          \begin{itemize}
          \item Involved in promoting IEC-61850 as the standard for substation
                automation and smart grid.
          \item Made proposals for power monitoring systems and MV \&
                LV switchgear and controlgear.
          \end{itemize}
    \end{itemize}
    \bigskip

    % Siemens - Automation Engineer
    {\bf Siemens Automation and Drives} \hfill {\em Feb 2007 - July 2007} \\
    Automation Engineer \hfill {\em Dubai, UAE} \\
    \begin{itemize}
    \item \underline{\it Training:}
          \begin{itemize}
          \item Completed training courses in Simatic (PLC programming) and
                WinCC (SCADA).
          \end{itemize}
    \item \underline{\it Integration:}
          \begin{itemize}
          \item Integrated PLC with industrial equipment using Profibus and
                Profinet.
          \item Integrated PLC with motor management devices (Simocode) and
                variable frequency drives (Micromaster).
          \item Interfaced PLCs with touch screen, HMI and other
                peripherals/sensors.
          \end{itemize}
    \end{itemize}
    \bigskip

    % ETA Mechanical & Electrical - Intern
    {\bf ETA Mechanical and Electrical} \hfill {\em Jun 2005 - Aug 2005} \\
    Intern \hfill {\em Dubai, UAE} \\
    \begin{itemize}
    \item Easy access catalog library implementing Kaizen methodologies.
    \end{itemize}
    \bigskip

%%
% Education
%
\subsection*{\MakeUppercase{\bf Education}}
    \hrule
    \bigskip
    {\bf George Mason University - Fairfax} \hfill {\em Dec 2010} \\ 
    M.S. in Electrical Engineering \\
    Systems Architecture \bigskip \\

    {\bf Birla Institute of Technology and Sciences - Pilani}
    \hfill {\em July 2007} \\ 
    B.E. (Hons.) Electrical \& Electronics Engineering \bigskip \\

%%
% Certifications
%
\subsection*{\MakeUppercase{\bf Certifications}}
    \hrule
    \bigskip
    \begin{itemize}
    \item KEMA: IEC 61850 training course
    \item Simatic S7: Programmable Logic Controller(PLC) Programming
    \item Siemens WinCC: SCADA software
    \end{itemize}
    \bigskip

\end{document}
